Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-08-17 nir_companions.tex
Formating software names

The observations were reduced using a custom reduction pipeline~\citep{figueira_radial_2010}. Written in IRAF's CL\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, {Inc.}, under cooperative agreement with the National Science Foundation.}~\citep{tody_iraf_1993} it provides for automated dark and non-linearity corrections (using the non-linearity coefficients provided by ESO), as well as the flagging and replacement of bad pixels. The images were corrected from sensitivity variations by dividing by a flat-field corrected from the blaze function effect. The nodding pairs were mutually subtracted and the order tracing was fitted by {\rd{} linear or cubic splines selected for each detector}.

@@

The continuum normalization and nod combining steps were also performed using IRAF while the following post reduction procedures and analysis all utilize \emph{Python}. This pipeline was chosen over the ESO CRIRES pipeline because it seemed relatively simple to use, being semi-automated, and appeared to have less bad pixel/cosmic ray artefacts in the extracted spectra. In hindsight this was not the case, with the removal of the extended artefacts that appeared.

@@

We note that there are many variations on this wavelength-calibration technique including those integrated within programs such as \emph{TelFit}~\citet{gullikson_correcting_2014}, and ESOs \emph{Molecfit}~\citet{smette_molecfit_2015}, that perform telluric correction and re-calibrate the wavelength axis themselves. {\rd{} Including concurrent fitting of a stellar spectral model, adjusted for RV, along with the telluric model could help to improve the wavelength calibration preformed here. For example~\citet{piskorz_evidence_2016} use only a telluric line model at other nIR wavelengths but needed to include a stellar model specifically around 2\,$\mu$m where the telluric lines are weaker.}

@@

After the telluric correction is performed, the spectra are corrected for Earth's barycentric RV using the \emph{helcor} PyAstronomy\footnote{https://pyastronomy.readthedocs.io} function ported from the REDUCE IDL package (See~\citet[][]{piskunov_new_2002}).

@@

The spectral model libraries were accessed using the useful ``grid tools'' interface provided in the \emph{Starfish}\footnote{\url{https://github.com/iancze/Starfish}} Python package~\citep{czekala_constructing_2015}, which made it efficient to load in the spectra when needed.

@@

\subsection{\texorpdfstring{\(\chi^{2}\)}\ \ method}
\label{subsec:chi2}
The well known \(\chi^{2} \) technique measures the weighted sum of the squared deviation between the observation (\({O}_{i}\)) and the computed models (\(C_{i}\)), with the minimum \(\chi^2\) value representing the best-fit parameters.
\[\chi^{2} = {\Sigma}_i { (O_{i} - C_{i})}^2 / {\sigma}_{i}, \] where \({\sigma}_{i}\) is the error on each measurement. We estimate the \(\sigma\) of each spectrum using the \(\beta\sigma\) method~\citep{czesla_posteriori_2018}, using the MAD (median absolute deviation about the median) robust estimator. {\rd{} This method estimates the spectral noise using numerical derivatives of the spectra. We followed the procedure outlined in~\citet{czesla_posteriori_2018}, analysing the results from successive parameter combinations to settle on an order of approximation (derivative level) of 5, and a jump parameter (pixels skipped to avoid correlations) of 2.} We apply the same \(\sigma\) value to all points \({\sigma}_{i} = \sigma\). The \(\beta\sigma\) method provided \(\sigma\) estimates for the target spectra which correspond inversely to signal-to-noise ratios between 100--500, {\rd{} similar to the values given in Table~\ref{tab:observations} calculated from the continuum of detector 2.}

@@

The inverse survival function of the \(\chi^2\) distribution is used to determine the confidence levels on the minimum \(\chi^2\) parameters. The inverse survival function returns a \(\Delta\chi^2\) value from the minimum \(\chi^2\) value for a given sigma level and degree of freedom\footnote{In \emph{Python} with the \emph{scipy} package this is a single line \texttt{scipy.stats.chi2(dof).isf(1-p)}, where \(p = 0.68\) for 1-\(\sigma\), and dof is the degree of freedom.}.
For example, the \(\Delta \chi^2\) for a single degree of freedom required for the 1-, 2-, and 3-\(\sigma\) levels is 1, 4, and 9 respectively~\citep{bevington_data_2003}. This method assumes that the measured flux is observed with a SNR sufficiently high so that the noise on the spectrum is approximately Gaussian, and the \(\chi^2\) method appropriate.

@@

However, we did not incorporate any interpolation into the companion recovery at this stage. This could be something to be added in the future to refine the recovered parameters, and to help the transition between the grid logg values. Codes are readily available to perform spectral interpolation which could be utilized for this, two of them are \emph{pyterpol}\footnote{https://github.com/chrysante87/pyterpol}~\citet{nemravova_xtauri_2016} and \emph{Starfish}\footnote{https://github.com/iancze/Starfish}~\citep{czekala_constructing_2015}.

\subsection{Future implementation}
\label{subsec:future}
\subsubsection{High resolution instrumentation}
\label{subsubsec:highres}
The future of high resolution near- and mid- IR spectrographs is looking bright, with many new ground- and space-based instruments currently being developed. Notable examples include CARMENES (550--1710~nm, R=82\,000) which is now operational~\citep{quirrenbach_carmenes_2014}, while SPIRou (980--2350~nm, R=73\,500)~\citep{artigau_spirou_2014} and NIRPS (970--1810~nm, R=100\,000)~\citep{bouchy_nearinfrared_2017} are still being assembled and installed. The eagerly awaited JWST \textbf{cite} will also be launched soon\footnote{Recently pushed to around May 2020} providing observations in both the near-IR (600--5300~nm, R=2700) and mid-IR (4900--28\,800~nm, R$\sim$1550--3250) regions without contamination from our atmosphere.

@@

{\rd{}  The recent work of~\citet{piskorz_evidence_2016} use a PCA technique to correct for the telluric spectra by applying it to several (number not specified) AB nodding pairs over their 60--180 minute integration time. We are uncertain if this technique would work as effectively on our observations due to our shorter integration time (24 minutes) would have less telluric variation present across the 8 nod spectra. A recent comparison of three telluric correction methods, \emph{Molecfit} and {TelFit} and {TAPAS} to the standard star method by (Ulmer-moll et al. (in preparation)) %~\cite[][in prep.]{ulmer-moll_telluric_2018}
 found that all three synthetic models preform better at correcting for atmospheric H$_2$O compared to the standard star method with \emph{Molecfit}, being a more complete tool, preforming slightly better over TAPAS.}

@@

This work was supported by Funda\c{c}\~ao para a Ci\^encia e a Tecnologia (FCT) (Portugal) research grants through national funds and from FEDER through COMPETE2020 by the following grants: UID/FIS/04434/2013 \& POCI--01--0145-FEDER--007672, PTDC/FIS-AST/1526/2014 \& POCI--01--0145-FEDER--016886, and PTDC/FIS-AST/7073/2014 \& POCI-01-0145-FEDER-016880.
J.J.N. acknowledges support from FCT though the PhD::Space fellowship PD/BD/52700/2014.
P.F., N.C.S. acknowledge support from FCT through Investigador FCT contracts IF/01037/2013CP1191/CT0001, IF/01312/2014/CP1215/CT0004, IF/00169/2012/CP0150/CT0002, and IF/00028/2014/CP1215/CT0002. P.F. further acknowledges support from FCT in the form of an exploratory project of reference IF/01037/2013CP1191/CT0001.
This work made use of PyAstronomy\footnote{PyAstronomy can be found at \url{https://pyastronomy.readthedocs.io}} and many other open source and under-credited software packages numpy, scipy, astropy, Starfish to name a few.
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France.

@@

    \label{appendix:A2}
    We applied the spectral differential procedure outlined above on the wavelength-calibrated and telluric-corrected CRIRES observations. The spectra were corrected for Earth's barycentric RV using the \emph{helcor} PyAstronomy\footnote{https://pyastronomy.readthedocs.io} function ported from the REDUCE IDL package (See~\citet[][]{piskunov_new_2002}) and Doppler shifted to the rest frame velocity of the system. The spectra were then subtracted from each other and analysed as described above.

>>>>

The observations were reduced using a custom reduction pipeline~\citep{figueira_radial_2010}. Written in \textsc{iraf}'s \textsc{cl}\footnote{\textsc{Iraf} is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, {Inc.}, under cooperative agreement with the National Science Foundation.}~\citep{tody_iraf_1993} it provides for automated dark and non-linearity corrections (using the non-linearity coefficients provided by ESO), as well as the flagging and replacement of bad pixels. The images were corrected from sensitivity variations by dividing by a flat-field corrected from the blaze function effect. The nodding pairs were mutually subtracted and the order tracing was fitted by {\rd{} linear or cubic splines selected for each detector}.

@@

The continuum normalization and nod combining steps were also performed using \textsc{iraf} while the following post reduction procedures and analysis all utilize \textsc{python}. This pipeline was chosen over the ESO CRIRES pipeline because it seemed relatively simple to use, being semi-automated, and appeared to have less bad pixel/cosmic ray artefacts in the extracted spectra. In hindsight this was not the case, with the removal of the extended artefacts that appeared.

@@

We note that there are many variations on this wavelength-calibration technique including those integrated within programs such as \textsc{TelFit}~\citet{gullikson_correcting_2014}, and ESOs \textsc{Molecfit}~\citet{smette_molecfit_2015}, that perform telluric correction and re-calibrate the wavelength axis themselves. {\rd{} Including concurrent fitting of a stellar spectral model, adjusted for RV, along with the telluric model could help to improve the wavelength calibration preformed here. For example~\citet{piskorz_evidence_2016} use only a telluric line model at other nIR wavelengths but needed to include a stellar model specifically around 2\,$\mu$m where the telluric lines are weaker.}

@@

After the telluric correction is performed, the spectra are corrected for Earth's barycentric RV using the \textsc{helcor} \textsc{PyAstronomy}\footnote{https://pyastronomy.readthedocs.io} function ported from the \textsc{reduce idl} package (See~\citet[][]{piskunov_new_2002}).

@@

The spectral model libraries were accessed using the useful ``grid tools'' interface provided in the \textsc{Starfish}\footnote{\url{https://github.com/iancze/Starfish}} \textsc{python} package~\citep{czekala_constructing_2015}, which made it efficient to load in the spectra when needed.

@@

\subsection{\texorpdfstring{\(\chi^{2}\)}\ \ method}
\label{subsec:chi2}
The well known \(\chi^{2} \) technique measures the weighted sum of the squared deviation between the observation (\({O}_{i}\)) and the computed models (\(C_{i}\)), with the minimum \(\chi^2\) value representing the best-fit parameters. The \(\chi^{2} \) is defined as
\begin{equation}
\chi^{2} = {\Sigma}_i { (O_{i} - C_{i})}^2 / {\sigma}_{i}\,,
\end{equation}
  where \({\sigma}_{i}\) is the error on each measurement. We estimate the \(\sigma\) of each spectrum using the \(\beta\sigma\) method~\citep{czesla_posteriori_2018}, using the MAD (median absolute deviation about the median) robust estimator. {\rd{} This method estimates the spectral noise using numerical derivatives of the spectra. We followed the procedure outlined in~\citet{czesla_posteriori_2018}, analysing the results from successive parameter combinations to settle on an order of approximation (derivative level) of 5, and a jump parameter (pixels skipped to avoid correlations) of 2.} We apply the same \(\sigma\) value to all points \({\sigma}_{i} = \sigma\). The \(\beta\sigma\) method provided \(\sigma\) estimates for the target spectra which correspond inversely to signal-to-noise ratios between 100--500, {\rd{} similar to the values given in Table~\ref{tab:observations} calculated from the continuum of detector 2.}

@@

The inverse survival function of the \(\chi^2\) distribution is used to determine the confidence levels on the minimum \(\chi^2\) parameters. The inverse survival function returns a \(\Delta\chi^2\) value from the minimum \(\chi^2\) value for a given sigma level and degree of freedom\footnote{In \textsc{python} with the \textsc{scipy} package this is a single line \texttt{scipy.stats.chi2(dof).isf(1-p)}, where \(p = 0.68\) for 1-\(\sigma\), and dof is the degree of freedom.}.
For example, the \(\Delta \chi^2\) for a single degree of freedom required for the 1-, 2-, and 3-\(\sigma\) levels is 1, 4, and 9 respectively~\citep{bevington_data_2003}. This method assumes that the measured flux is observed with a SNR sufficiently high so that the noise on the spectrum is approximately Gaussian, and the \(\chi^2\) method appropriate.

@@

However, we did not incorporate any interpolation into the companion recovery at this stage. This could be something to be added in the future to refine the recovered parameters, and to help the transition between the grid logg values. Codes are readily available to perform spectral interpolation which could be utilized for this, two of them are \textsc{pyterpol}\footnote{https://github.com/chrysante87/pyterpol}~\citet{nemravova_xtauri_2016} and \textsc{Starfish}\footnote{https://github.com/iancze/Starfish}~\citep{czekala_constructing_2015}.

\subsection{Future implementation}
\label{subsec:future}
\subsubsection{High resolution instrumentation}
\label{subsubsec:highres}
The future of high resolution near- and mid- IR spectrographs is looking bright, with many new ground- and space-based instruments currently being developed. Notable examples include CARMENES (550--1710~nm, R=82\,000) which is now operational~\citep{quirrenbach_carmenes_2014}, while SPIRou (980--2350~nm, R=73\,500)~\citep{artigau_spirou_2014} and NIRPS (970--1810~nm, R=100\,000)~\citep{bouchy_nearinfrared_2017} are still being assembled and installed. The eagerly awaited \textit{JWST} \textbf{cite} will provide observations in both the near-IR (600--5300~nm, R=2700) and mid-IR (4900--28\,800~nm, R$\sim$1550--3250) regions without contamination from our atmosphere.

@@

{\rd{}  The recent work of~\citet{piskorz_evidence_2016} use a PCA technique to correct for the telluric spectra by applying it to several (number not specified) AB nodding pairs over their 60--180 minute integration time. We are uncertain if this technique would work as effectively on our observations due to our shorter integration time (24 minutes) would have less telluric variation present across the 8 nod spectra. A recent comparison of three telluric correction methods, \textsc{Molecfit} and \textsc{TelFit} and {TAPAS} to the standard star method by (Ulmer-moll et al. (in preparation)) %~\cite[][in prep.]{ulmer-moll_telluric_2018}
 found that all three synthetic models preform better at correcting for atmospheric H$_2$O compared to the standard star method with \textsc{Molecfit}, being a more complete tool, preforming slightly better over TAPAS.}

@@

This work was supported by Funda\c{c}\~ao para a Ci\^encia e a Tecnologia (FCT) (Portugal) research grants through national funds and from FEDER through COMPETE2020 by the following grants: UID/FIS/04434/2013 \& POCI--01--0145-FEDER--007672, PTDC/FIS-AST/1526/2014 \& POCI--01--0145-FEDER--016886, and PTDC/FIS-AST/7073/2014 \& POCI-01-0145-FEDER-016880.
J.J.N. acknowledges support from FCT though the PhD::Space fellowship PD/BD/52700/2014.
P.F., N.C.S. acknowledge support from FCT through Investigador FCT contracts IF/01037/2013CP1191/CT0001, IF/01312/2014/CP1215/CT0004, IF/00169/2012/CP0150/CT0002, and IF/00028/2014/CP1215/CT0002. P.F. further acknowledges support from FCT in the form of an exploratory project of reference IF/01037/2013CP1191/CT0001.
This work made use of \textsc{PyAstronomy}\footnote{PyAstronomy can be found at \url{https://pyastronomy.readthedocs.io}} and many other open source and under-credited software packages numpy, scipy, astropy, Starfish to name a few.
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France.

@@

    \label{appendix:A2}
    We applied the spectral differential procedure outlined above on the wavelength-calibrated and telluric-corrected CRIRES observations. The spectra were corrected for Earth's barycentric RV using the \textsc{helcor} PyAstronomy\footnote{https://pyastronomy.readthedocs.io} function ported from the REDUCE IDL package (See~\citet[][]{piskunov_new_2002}) and Doppler shifted to the rest frame velocity of the system. The spectra were then subtracted from each other and analysed as described above.
